A Multi-Modal Model of Object Deformation for Robotic Pushing

### 2016-09-09 AnswersToComments.tex
changed letter

\opening{Dear Dr. Ricardo Téllez,}

@@

We thank the reviewer for the comments and we have made our best effort to address them.  In the following text we explain in some detail the changes we did.

Before that, we also wish to apologise because, in spite of our efforts, we still have not been able to implement the comparison with other existing methods, as any fair comparison requires an extension/implementation to closely related methods which do not work under the same conditions that ours.  We are working on that, but the deadline has come and we will submit our work leaving only this point pending.  If you could allow us to submit another version in four weeks, we should be able to include this comparison.

Thank you very much for everything,

@@

\vspace{2cm}

Reviewer(s)' Comments to Author:

Reviewer: 1

Comments to the Author

This article aims at tracking three-dimensional deformable objects under robot motion and predicting the force causing the deformation.

%\marker
%\comment{While this is entirely correct we would like to say that this was not the intended emphasis of the article. The article primarily aims at predicting both the force and the deformation.  The tracking of the shape is used only during training as part of the evaluation function, it is not the goal. We apologise in case this wasn't clear, probably it was. Nevertheless we have revised the paper throughout to try to make this clearer.}
%

For these purposes, the authors propose two models, including an extension of the mass-spring model and a regression model, where the parameters of the mass-spring model are learned with an evolutionary searching algorithm on visual data and force data, and the parameters of the regression model are learned with least-square methods on stress-strain graph. These models are tested on a sponge and a plasticine, and evaluated based on the balanced F-score. The results are presented both quantitatively and qualitatively.

@@

4, section IV-D is not explained: what is the relation between "collision detection" and the proposed model?

@@

\marker
%\comment{TODO: Move section IV-E after IV-A but must emphasize that the geometric constraints in IV-A are enforced through energy preservation, while those in IV-E have immediate effects on the triangulations without directly affecting the equations.}
\comment{TODO: Chage title of section E to ``Geometric constraints outside from the mass-spring model''.  ``Even with the addition of the term for preservation of angles to the mass-spring simulation...''}

\comment{Thank you for the observation, it shows the paper was not fully explaining the difference between the constraints presented in section IV-A and those in section IV-E.  The first belong to the mass-spring model (as everything being explained in subsections A to C).  The routines in section IV-E are independent and more closely related to mesh-related fixes like the one explained in section IV-D.  We changed the title of section IV-E to reflect this and further explained this difference in its text.}

@@

\marker
3, in line 58 of page 1, the authors claim "In each case the models can be run in two modes, prediction and classification". But the classification mode is not explained later, but a filtering mode is included instead. Besides, please clearly illustrate the mentioned modes and processes in Figure 2.

\comment{What does he mean by ``filtering mode instead''?}

@@

\comment{Since it was not clear the wording of the first paragraph of section IV-A was modified, where the general idea is explained, the details come in later paragraphs.}

@@

\comment{Added an introduction at the beginning of section IV.}

@@

\comment{The term was introduced on the second paragraph of section IV.}

@@

\comment{Added explanation that it happens when/because we use $C$s that model springs.}

@@

\comment{It is not within the scope of the article to explain that derivation, since it belongs to Teschner's model, however the reference to the article we got it from was repeated here.}

@@

\comment{Changed phrase for the explanation that Teschner gave.}

12, in line 50 of page 4, please explain "the angles between adjacent edges". As adjacent edges form one angle, do the authors mean adjacent angles? Similar ambiguity exists in line 2 of page 5.

@@

\comment{Reworded sentence to add more detail.}

@@

\comment{Explained in more detail and changed notations to make it consistent with previous paragraphs.}

@@

\comment{Improved the description across the whole subsection.}

@@

\comment{No, it can be found across the web in many sites.  We changed the word ``common'' in the text, for ``standard'', which should emphasise more this fact.}

@@

\comment{Section V-B? Added a justification at the beginning of the section.  The meaning of $\alpha, \beta, \gamma, \zeta$ was covered on lines 7,9,10,11 but a shorter description was added when they are firstly introduced.}

@@

\comment{Changed paragraph.}

@@

\comment{Reference added.  Relationship with active contour explained.}

@@

\comment{Added the name ``F-score'' and an equation to define $\mu(f)$}

@@

\comment{Added information.}

\marker
23, in the experiments, please compare with other existing methods.

@@

\comment{Added explanations}

@@

\comment{Sorry, I don't understand this one.  There are three lines with markers: square, circle and triangle.  Those represent experimental data (ground data).  The other two do not have markers because those are regression lines (predictions), but they have different colours.  Are these ones you mention as ``lines with the same marker''?}

@@

\comment{Yes, it is $h$, the name of the variable was added.}

@@

\comment{Changed ``for novel interactions'' for a more concrete description.}

\comment{Here we are not focusing on classifying static objects in new environments, but rather in classifying the material an object is made of when the entry is its behaviour in time.  Visually, the blocks are actually very similar prior to deformation, therefore the most relevant difference lies in their dynamic behaviour.  That is why the classification task looks different from traditional static datasets.  Instead of a large collection of labeled images in different backgrounds, we used six videos of two different materials and asked the system to identify which material it looks at through the videos.  The explanation in the article was modified to be more specific about this.}

@@

\comment{An explanation about "training", "test 1, test 2" was added.}

\comment{Since there are only two materials the number of false positives for one material is exactly the false negatives for the other material, that is why we considered that recall would be redundant.}

@@

\comment{Added to the background section, alongside the statement ``those predictions are used only for the next frame and can not be used for robotic planning, where predictions must be done for several frames ahead''}

I look forward to hearing from you.

>>>>

\opening{Dear Dr. Ricardo Téllez, Dr Guillem Aleny\`{a},}

@@

We would like to thank the reviewer for their insightful comments, which have enabled us to significantly improve our paper. We have made our best effort to address them.  In the following pages we explain in some detail the changes we made. We have also suggested a slight change to the title make it clear, as the reviewer pointed out, that the paper deals solely with pushing actions and not manipulation in general.

Before we detail the precise changes made, we also wish to apologise because, in spite of our efforts, we still have not been able to implement the requested comparison with another existing method, as any fair comparison requires an extension to the compared method(s). This extension is necessary because none of the methods were designed to work under qualitatively the same conditions as ours.  Because of this we are still working on an extension of another method, and its implementation. We expect to complete it within a month. To this end, we wrote to you to request an extension, but we have not yet received a reply. Therefore, to conform to the deadline we were given, we are submitting the paper with all the textual revisions completed. We would like to submit a further version that includes the results of our comparison. We request an extension of four weeks to allow this. Please let us know at your convenience whether this is acceptable.

All of the changed parts of the manuscript have been highlighted in red in the re-submitted version. We also made some minor changes to the grammar in addition to the requested changes. We have not marked these.

We thank you again for your very helpful comments on our paper. They have helped us to significantly improve it. We hope that we have satisfactorily addressed all your requested changes to the text. We will submit a second revision with the experimental comparison as soon as possible. We look forward to hearing from you.

@@

\newpage

Reviewer's Comments \comment{(and responses in blue)}:

This article aims at tracking three-dimensional deformable objects under robot motion and predicting the force causing the deformation.
%\marker
%\comment{While this is entirely correct we would like to say that this was not the intended emphasis of the article. The article primarily aims at predicting both the force and the deformation.  The tracking of the shape is used only during training as part of the evaluation function, it is not the goal. We apologise in case this wasn't clear, probably it was. Nevertheless we have revised the paper throughout to try to make this clearer.}
%
For these purposes, the authors propose two models, including an extension of the mass-spring model and a regression model, where the parameters of the mass-spring model are learned with an evolutionary searching algorithm on visual data and force data, and the parameters of the regression model are learned with least-square methods on stress-strain graph. These models are tested on a sponge and a plasticine, and evaluated based on the balanced F-score. The results are presented both quantitatively and qualitatively.

@@

\newpage 
4, section IV-D is not explained: what is the relation between "collision detection" and the proposed model?

@@

%\comment{TODO: Move section IV-E after IV-A but must emphasize that the geometric constraints in IV-A are enforced through energy preservation, while those in IV-E have immediate effects on the triangulations without directly affecting the equations.}

\comment{Thank you for the observation. We would very much like to keep the separation of the two sections, as the two constraints are not at all the same, and the additional constraints in section IV-E are both optional and separate from those in the mass-spring model (section IV-A). Those belonging to the mass-spring model are soft-constraints implemented through an energy function. The additional routines in section IV-E are independent of the mass spring model.  These are hard constraints, being purely kinematic, and are rather more closely related to the collision detection techniques described in IV-D.  We changed the title of section IV-E to reflect this and further explained this difference in the text.}

@@

\newpage

3, in line 58 of page 1, the authors claim "In each case the models can be run in two modes, prediction and classification". But the classification mode is not explained later, but a filtering mode is included instead. Besides, please clearly illustrate the mentioned modes and processes in Figure 2.

\comment{We hope that we have now addressed this in the model overview section. We do not have a filtering mode as such. Instead we run models for each material in prediction model, and compare their predictions to the ground truth. This is the classification mode. This should now be much clearer, especially from the addition of new figures that show the prediction machine (Fig 3.) and the classification machine built on top of it (Fig 4.).}

@@

\comment{Since it was not clear the wording of the first paragraph of section IV-A has been modified, where the general idea is explained, the details come in later paragraphs.}

@@

\comment{We have added an introduction at the beginning of section IV.}

@@

\comment{The term was introduced in the second paragraph of section IV.}

@@

\comment{We have added an explanation that it happens when/because we use $C$s that model springs.}

@@

\comment{It is not within the scope of the article to explain that derivation, since it belongs to Teschner's model, and it would take too much space. We have, however included a reference to the article for the reader to follow up.}

@@

\comment{We have changed this phrase to make clearer the explanation that Teschner gave for this.}

\newpage 
12, in line 50 of page 4, please explain "the angles between adjacent edges". As adjacent edges form one angle, do the authors mean adjacent angles? Similar ambiguity exists in line 2 of page 5.

@@

\comment{We have re-worded the sentence to add more detail.}

@@

\comment{We have explained this in more detail and changed the notation to make it consistent with previous paragraphs.}

@@

\comment{We meant the collisions between both the deformed object and the finger, and between the deformed object and the table. We have now improved the description across the whole subsection to make this clear.}

@@

\comment{No, it can be found in many places.  We changed the word ``common'' in the text, for ``standard'', which should make this clear.}

@@

\comment{We have added this justification at the beginning of the section.  The meaning of $\alpha, \beta, \gamma, \zeta$ is covered in lines 7,9,10,11 of Algorithm 5. We have also added a short description in the main text when they are first introduced.}

@@

\comment{We have changed this paragraph to make it clear.}

@@

\comment{We have added a reference for this, and explained the relationship with active contours.}

\newpage

@@

\comment{Thanks. We now use the name ``F-score'' and include an equation to define $\mu(f)$}

@@

\comment{We have added information on both these points.}

23, in the experiments, please compare with other existing methods.

\comment{We are still working on this. We requested an extension, as this requires more time than we had available to do the revisions. We haven't received a reply to date. So we are submitting the paper with the textual changes now. If these textual changes are satisfactory we will submit a second revision with the comparison as soon as possible. We estimate this will take four weeks from today. We are sorry that despite our best efforts this has taken longer that we expected.}

@@

\comment{We have added explanations of these values.}

@@

%\comment{Sorry, I don't understand this one.  There are three lines with markers: square, circle and triangle.  Those represent experimental data (ground data).  The other two do not have markers because those are regression lines (predictions), but they have different colours.  Are these ones you mention as ``lines with the same marker''?}

@@

\comment{Yes, it is $h$, the name of the variable has been added to make this clear.}

@@

\comment{We have replaced ``for novel interactions'' with a more concrete description.}

\comment{Here we are not focusing on classifying static objects in new environments, but rather in classifying the material an object is made of when the entry is its behaviour in time.  Visually, the blocks are actually very similar prior to deformation, therefore the most relevant difference lies in their dynamic behaviour.  That is why the classification task looks different from traditional static datasets.  Instead of a large collection of labeled images in different backgrounds, we used six videos of two different materials and asked the system to identify which material it looks at through the videos.  The explanation in the article has been modified to be more specific about this.}

\newpage

@@

\comment{An explanation about "training", "test 1, test 2" has been added.}

\comment{Since there are only two materials, the number of false positives for one material is exactly the number of false negatives for the other material, that is why we considered that recall would be redundant.}

@@

\comment{We have added references on deformable object tracking to the background section. We have also made clear why the use o one-step prediction in those algorithms is different from our multi-step prediction problem. }
